Providing a Unified Software Environment for Canada’s National Advanced Computing Centers

### 2019-03-21 paper.tex
added references to figures to be added and a description of the layered approach for System/Nix/EasyBuild

\subsection{CVMFS structure}
\label{sub:CVMFS_structure}
CVMFS is designed similarly to the Network Time Protocol stratum model. There is one source of truth called the stratum 0, where software is injected.  The stratum 0 is never accessed directly by clients. If it fails, the only immediate consequence is that injection of new files is not possible until it is back online.

@@

\subsection{Deployment of CVMFS in Compute Canada}
\label{sub:CVMFS_in_CC}
For Compute Canada's needs, we have deployed three CVMFS repositories, each composed of a stratum 0 and one or multiple strata 1.

@@

>>>>

\subsection{CVMFS structure}
\label{sub:CVMFS_structure}
CVMFS is designed similarly to the Network Time Protocol stratum model, as illustrated in Figure~\ref{fig:CVMFS_structure}. There is one source of truth called the stratum 0, where software is injected.  The stratum 0 is never accessed directly by clients. If it fails, the only immediate consequence is that injection of new files is not possible until it is back online.

@@

\textbf{TODO: Insert figure representing the CVMFS structure of strata. }
\label{fig:CVMFS_structure}

\subsection{Deployment of CVMFS in Compute Canada}
\label{sub:CVMFS_in_CC}
For Compute Canada's needs, we have deployed three CVMFS repositories, each composed of a stratum 0 and one or multiple strata 1. This allows us to follow a workflow that includes testing before exposing software packages to user, as illustrated in Fig~\ref{fig:Workflow}.

@@

\textbf{TODO: INSERT FIGURE representing our workflow (build => test locally => dev => test on cluster => prod) }
\label{fig:Workflow}

\section{A layered approach}
\label{sec:Layered_environment}
To install software packages for our common environment, we follow a layered approach, as illustrated in Table~\ref{tab:layers}. First, we require a basic Linux installation. Any version of Linux with a kernel 2.6.32 or more recent should work. This layer is managed by the system administrators, and should contain any driver, such as GPU drivers or drivers for the network fabric, kernel modules, as well as privileged binaries.

The second layer is what we call our compatibility layer. It contains almost all packages that one would typically install with the Linux distribution's package manager, such as {\it yum} or {\it apt-get}.

The third layer is the scientific application layer. It contains mostly scientific or performance critical applications, including for example MPI implementations, CUDA, mathematical libraries, and domain specific applications.

\textbf{TODO: INSERT FIGURE/TABLE WITH OS layer, Nix layer, EasyBuild layer}
\label{tab:layers}
